---
title: "National Trust Properties Map"
author: "Ashley You"
date: "13 August 2017"
output: html_document
---

National Trust is a conservation organisation in England, Wales and Northern Ireland, and the largest membership organisation in the United Kingdom. In Scotland, there is an independent National Trust for Scotland. 

The map I created with Leaflet shows locations of properties owned by National Trust in England, Wales, Northern Ireland and Scotland.  

# Load libraries 

```{r, message=FALSE, warning=FALSE}
library(leaflet)
library(htmltools)
```

# Make the Map 

```{r, message=FALSE, warning=FALSE}
data <-  read.table("nationaltrust.txt",quote=NULL,comment="", sep="\t",header=TRUE)  


NT_icon <- makeIcon(iconUrl = ifelse(data$Region=="Scotland","https://upload.wikimedia.org/wikipedia/commons/e/ea/National_Trust_for_Scotland.svg", "https://upload.wikimedia.org/wikipedia/en/thumb/1/11/NationalTrustUKLogo.svg/512px-NationalTrustUKLogo.svg.png"),
         iconWidth = 20*215/230, 
         iconHeight = 25,
         iconAnchorX = 20*215/230/2, 
         iconAnchorY = 16)

leaflet(data) %>% 
        addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
        addMarkers(~Lng,~Lat,popup= ~htmlEscape(paste(Place,"- Postcode:",Postcode)), clusterOptions=markerClusterOptions(),icon = NT_icon)

```
